QPLIB: A Library of Quadratic Programming Instances

### 2017-01-27 conclusion.tex
Add files via upload

 This manuscript describes the first comprehensive library of instances for Quadratic Programming (QP). Since QP comprises  different and `varied'' categories of problems, we propose a classification and then we describe the principal solution methods representing the state-of-the-art algorithms for QP.

We then describe the steps of the adopted process used to filter the gathered instances  in order to build the new library. The goals we purposed are of different natures and we tried to build a library which is computationally challenging and as broad as possible, i.e., it represents the largest possible categories of QP problems.

>>>>

 This manuscript describes the first comprehensive library of instances for Quadratic Programming (QP). Since QP comprises  different and ``varied'' categories of problems, we propose a classification and we briefly discuss the main classes of solution methods for QP.

We then describe the steps of the adopted process used to filter the gathered instances  in order to build the new library. The goals we purposed are of different natures and we tried to build a library which is computationally challenging and as broad as possible, i.e., it represents the largest possible categories of QP problems, while remaining of manageable size.
